Distribution of a Facebook application

### 2011-04-08 paper.tex
implementation and data evaluation

\subsection{Implementation}
\label{sec:implementation}
The quiz-application detailed in the last section makes use of
Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}. It requires
permissions for \textit{user$\_$birthday} and \textit{publish$\_$stream}.
Data used by the quiz are stored in a MySQL-database, tables have the
following contents:
\begin{itemize}
\item \textbf{User} - entries are created for each user who participates as
well as for each of a user's friends. A flag details if user
participated or not.
\item \textbf{Friendships} - creates entries for each friendship found in
users' friend lists.
\item \textbf{Questions} - contains the questions of the quiz.
\item \textbf{Answers} - contains the possible answers and a flag to mark them
as correct or false.
\item \textbf{Given answers} - stores each answer given by a user.
\item \textbf{User score} - stores the score user had in the quiz.
\item \textbf{Correct answered questions} - stores which questions were correct
answered by which user.
\end{itemize}

The database queries are performed with the PHP
pear\footnote{http://pear.php.net/}-package. The script which performs
the queries uses few files: The index.php manages the application
flow. The library.php contains all the functions needed, and quiz.php,
question.php, and quizResult.php display the quiz as well as the
correct solution and the feature to invite friends.

\subsection{Data collection}
\label{sec:data-coll-eval}

\subsection{Data evaluation}
\label{sec:data-evaluation}

>>>>

\subsection{Implementation}
\label{sec:implementation}
The quiz-application detailed in the last section makes use of
Facebook's php-\ac{sdk} and JavaScript-\ac{sdk}. It requires
permissions for \textit{user$\_$birthday} and
\textit{publish$\_$stream}.
Data used by the quiz are stored in a MySQL-database, and php scripts
handle the application flow. \textit{index.php} maintains calls of
scripts printing the quiz (\textit{quiz.php}, \textit{question.php}), and displaying
the correct solution as well as the opportunity to invite friends
after completion of the quiz
(\textit{quizResult.php}). \textit{library.php} contains all the
functions needed.

\subsubsection{Database schema}
\label{sec:database-schema}
The database queries are performed with PHP
pear\footnote{http://pear.php.net/}-package. The following tables exist:
\begin{itemize}
\item \textbf{User} - entries are created for each user who participates as
well as for each of a user's friends. A flag details if user
participated or not.
\item \textbf{Friends} - creates entries for each friendship found in
users' friend lists.
\item \textbf{Questions} - contains the questions of the quiz.
\item \textbf{Answers} - contains the possible answers and a flag to mark them
as correct or false.
\item \textbf{GivenAnswers} - stores each answer given by a user.
\item \textbf{UserScore} - stores the score user had in the quiz.
\item \textbf{CorrectAnsweredQuestions} - stores which questions were correct
answered by which user, and which were not.
\end{itemize}

\subsubsection{Application flow}
\label{sec:application-flow}
When a user enters, the \textit{OAuth Dialog} is started. Then, the user data
including gender, birthday, name, Facebook-ID are stored together with
a timestamp, and column \textit{has-used-app} is set to 1. In
addition, each user's friends are also stored and column
\textit{has-used-app} is set to 0. Then, friendships are stored in the
table \textit{friends}. Next, the quiz is created by randomly choosing
five questions from the questions table and requiring the answers. To
make the questions more attractive, the name of an image convenient to
the questions topic is also stored in the questions table, and this
image is placed on the left side of each question. Since multiple
selection is possible, before the answers, which are also queried from
the MySQL database, checkboxes are placed before each answer.

As soon as a user completed the quiz, evaluation starts by checking
which questions were answered correctly and by computing the final
score. Due to multiple selection, user answers are stored in
an multidimensional array and compared with another multidimensional
array containing the correct solution and created from the database.
The given answers are then stored, and in addition, in another table
(\textit{correctAnsweredQuestions)}
it is only stored which questions were correct and incorrect answered.
Some user join the quiz multiple times, and for this reason, each
score they had is stored in a score table. The user table is also
changed by entering or updating the average score, computed from each all the scores stored
in the score table. Then, by using the Java Script \ac{sdk}, the user
get the option to post the results onto their Facebook wall.

In order to make the whole thing challenging, it
is then computed how high the user's score is compared to the friends
and to all the other users. 
In addition, the correct solutions are given, and if a user knew the
right answer, a green check is placed left to the question. Otherwise,
a red cross is displayed at the same place. At least, the table with
the friendships and table \textit{correctAnsweredQuestions} are used
to identify friends  which answered the question correctly. Images of
them are placed beyond each question's solution together with the
information that those friends knew the right solution. 
In the end, users get the chance to invite friends to the app to
challenge them. For this reason, each friend's picture is added and
user can click at them. On click, a pre-defined function from
Facebook's Java Script \ac{sdk} is called to perform the invitation.

\subsection{Data evaluation}
\label{sec:data-evaluation}
Data evaluation is also performed by using the MySQL tables, and
PHP. In addition, the dot
language\footnote{http://www.graphviz.org/Documentation.php} is used
to create graphs.

The evaluation scripts are maintained by \textit{main.php}. A user
class represents Facebook's social graph internally. Properties of
user objects equal the \textit{user}-table's properties, and a user's
friendships are represented by a list of references to corresponding
user objects. The whole set of users is maintained by
\textit{main.php}, where they are stored in an array. Class \textit{Graph}
allows for output of various graphs in dot-language created from the
internal social graph.
